### 2023-04-30 chapter2/chapter2.tex
Re-phrased last paragraph slightly

However, as IDRs likely evolve under multiple selective regimes where the constraint of different compositional, patterned, or motif features is highly specific to each, we expect a combination of statistical and computational methods will be needed to disentangle the complex forces driving IDR evolution. Accordingly, while these results represent a significant step forward in relating sequence to function in IDRs, further studies exploring these and other approaches will undoubtedly reveal new insights into these pervasive but poorly understood regions of proteins.

>>>>

However, as IDRs are likely subject to multiple selective pressures where the constraints on different compositional, patterned, or motif features is highly specific to each, we anticipate a range of computational and experimental methods will be needed to disentangle the complex forces driving IDR evolution. Accordingly, while these results represent a significant step forward in relating sequence to function in IDRs, further studies exploring these and other approaches will undoubtedly reveal new insights into these pervasive but poorly understood regions of proteins.
